---
title: "TimeSeries"
author: "Amit Kr Pradhan"
date: "12/7/2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Time Series Forcasting
Time series forcasting with Air passenders data.

```{r Airpassengers}
summary(AirPassengers)
```

## Including Plots

Lets plot the data

```{r pressure, echo=TRUE}
plot(AirPassengers)
abline(reg = lm(AirPassengers~time(AirPassengers)))
```
## Lets check the data formar.
```{r}
str(AirPassengers)
```
```{r}
#Start date of timeseries
start(AirPassengers)
#End date of timeseries
end(AirPassengers)
#frequency of time i.e. 12 months
frequency(AirPassengers)

```
## Box plot to analyse the month when the traffic is maximum.
```{r}
boxplot(AirPassengers~cycle(AirPassengers))
```
Month of august the traffic is high. This way we check the seasonality of the data.
## To Make stationary
```{r}
# Use log function to make the variance equal.
plot(log(AirPassengers))
plot(diff(log(AirPassengers)))
```
# Modeling a time series model.
AR I MA :  Auro regressive Intigration moving average  
p d q
# autocorrelation graph
```{r}
acf(AirPassengers)
```

```{r}
# To determine q, i.e. movirage coefficient
# First line which get inverted select line. and select its previous as q.
acf(diff(log(AirPassengers)))
```

```{r}
# Determine p
# Similar to q select the first line which is inverted and select its previous as p. In this case p=1
pacf(diff(log(AirPassengers)))
```
# Now Lets model an ARIMA forcasting model
```{r}
fit <- arima(log(AirPassengers), c(0,1,1), seasonal = list(order = c(0,1,1), period = 12))
pred <- predict(fit, n.ahead = 10*12)
pred1 <- 2.718 ^ pred$pred
pred1
```

```{r}
ts.plot(AirPassengers,2.718^pred$pred, log = "y",lty = c(1,3))
```
```{r}
datawide<-ts(AirPassengers,frequency = 12, start = c(1949,1),end = c(1959,12))
fit1 <- arima(log(datawide),c(0,1,1),seasonal = list(order=c(0,1,1), period =12))
pred_a <- predict(fit1,n.ahead= 10*12)
pred2<-2.718^pred_a$pred
data2<-head(pred2,12)
data2

# Forcasted Data
predict_1960 = round(data2)
predict_1960

# Original Data
origin_1960 = tail(AirPassengers,12)
origin_1960



```

